\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{\textbf{Interview with volunteer}}
\author{Parkrun App}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\section*{Information}
\begin{itemize}[label=]
    \item \textbf{Name: Brian Godsman} 
    \item \textbf{Age: 53} 
\end{itemize}

\section*{Questions}
\begin{enumerate}[label=\textbf{Question \arabic*:}]
    \item How long have you been participating as a runner in Parkrun?\\
        \textit{10 years as a runner.}
    \item How long have you been a volunteer?\\
        \textit{7 years as a volunteer.}
    \item What motivates you most regarding the volunteer work?\\
        \textit{Giving back to the community. We all have to give back a bit in some ways. }
    \item Can you share some difficult moments you have encountered during your volunteer work?\\
        \textit{Haven't encountered any.}
    \item Is there some recurring part of the work that you feel can be made more efficient?\\
        \textit{Getting our material out on the track and getting everything ready for the event. In cold weather its really hard for the volunteers who stand by the finish line and scan codes etc. }
    \item Do you feel that a mobile app specifically designed for volunteers could make the work easier?\\
    \textit{If no, move on to Other thoughts}\\
        \textit{Yes}
    \item Are there any specific functionalities that such an app should provide?\\
        \textit{Less experienced volunteers need the help. The app would be mostly for new volunteers or people who volunteer rarely.}
    \item What mobile phone do you have? Brand, OS, model, etc. \\
        \textit{iPhone - iOS}
\end{enumerate}

\newpage
\section*{Design questions - show prototype}
\begin{enumerate}[label=\textbf{Question \arabic*:}]
    \item What are your thoughts on this login screen?\\
        \textit{The login page looks good, but I don't want to log in. Why should I have to log in? I don't want to register, simplify the app.}
    \item What do you think about this screen for account creation?\\
        \textit{not shown}
    \item What are your thoughts about the running events page/event map page?\\
        \textit{Need a lot more detail in the maps. AR is a bad idea, unreliable. Make the app easy to use. Don't want to use my phone when my hands are full of markers. Include pictures with the instructions. Checking markers as placed is unnecessary, don't want to get my phone out every time, there are 25 direction markers on the run or something close to that. \\
        The app needs to be simple. Step by step instructions would be great. }
    \item What are your thoughts on the colors and fonts?\\
        \textit{answer}
\end{enumerate}

\section*{Other thoughts}
\begin{itemize}[label=]
    \item Is there anything else you would like to add or any other thoughts?\\
    \textit{Another approach to the app (complete redesign): Make it an open  database where all park runs can store their information and descriptions for the volunteers. Its not like the information is in any way classified. This way the app would not need a log in except for the people adding things to the database.}
\end{itemize}
\thispagestyle{empty}

\end{document}