\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{\textbf{Interview with volunteer}}
\author{Parkrun App}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\section*{Information}
\begin{itemize}[label=]
    \item \textbf{Name: Angela} 
    \item \textbf{Age: 54} 
\end{itemize}

\section*{Questions}
\begin{enumerate}[label=\textbf{Question \arabic*:}]
    \item How long have you been participating as a runner in Parkrun?\\
        \textit{11 years}
    \item How long have you been a volunteer?\\
        \textit{11 years}
    \item What motivates you most regarding the volunteer work?\\
        \textit{I am a nurse, and it was sometimes recommended to my patient as a form of rehab etc, so I tried it and got hooked. It is a lovely community. Our parkrun id-number is unique, the only unique identification in the world. }
    \item Can you share some difficult moments you have encountered during your volunteer work?\\
        \textit{Sometimes people get injured, thats always hard. Nothing thats happened to me personally really. }
    \item Is there some recurring part of the work that you feel can be made more efficient?\\
        \textit{Different volunteers put signs in different spots. Better if everyone put them in the same place.}
    \item Do you feel that a mobile app specifically designed for volunteers could make the work easier?\\
    \textit{If no, move on to Other thoughts}\\
        \textit{Yes, especially for new volunteers.}
    \item Are there any specific functionalities that such an app should provide?\\
        \textit{Tell you here! when to place sign. Could be gps area that you have entered the area where the sign is to be placed.}
    \item What mobile phone do you have? Brand, OS, model, etc. \\
        \textit{An android phone.}
\end{enumerate}

\newpage
\section*{Design questions - show prototype}
\begin{enumerate}[label=\textbf{Question \arabic*:}]
    \item What are your thoughts on this login screen?\\
        \textit{Weird to register as volunteer - we are already volunteers.}
    \item What do you think about this screen for account creation?\\
        \textit{not asked}
    \item What are your thoughts about the running events page?\\
        \textit{Couldnt find where to press to enter the specific event page first. Needs to be more clear. }
    \item How do you feel about this event map page?\\
        \textit{It is a good thing to have checkpoints on the map for the markers etc.}
    \item What are your thoughts on the colors and fonts?\\
        \textit{not asked}
\end{enumerate}

\section*{Other thoughts}
\begin{itemize}[label=]
    \item Is there anything else you would like to add or any other thoughts?\\
    \textit{What about different courses? We have a winter course here for example. And also, there are two marshals, but three people who put up signs.}
\end{itemize}
\thispagestyle{empty}

\end{document}